The Galactic Midplane is Not a Plane: Implications for {\em Gaia}

### 2019-04-16 paper/ms.tex
Add Lz to deltaR-deltax discussion

There is a slight complication in the formula for computing $\Delta J_r/J_r$.
In a moment we will consider the effect of an inaccuracy in the distance from
the Sun to the Galactic center on actions. However, this inaccuracy induces an
error in $x$, or $\Delta x$. This is not the same as an inaccuracy in $\Delta
R$, but they are related by the following argument. An error $\Delta x$ will
induce an erroneous radius $R_{\text{err}}$ related by the formula,
\beq
(x+\Delta x)^2 + y^2 = R_{\text{err}}^2\text{.}
\eeq
Keeping only terms to first order in $\Delta x$, we have that,
\beq
\begin{split}
R_{\text{err}}^2 &= R^2 - 2 R \cos{\theta} \Delta x \\
\implies \Delta R &\equiv \abs{R_{\text{err}} - R} = \abs{\cos{\theta}} \Delta x\text{.}
\end{split}
\eeq
Averaging over the circle, we therefore have that
\beq
\avg{\Delta R} = \frac{2}{\pi} \Delta x\text{.}
\eeq
Therefore, the error in $J_r$ is related to $\Delta x$ by,
\beq\label{eq:Jr_epi_dx}
\frac{\Delta J_r}{J_r} = \frac{4 \Delta x}{\pi A_R}\text{.}
\eeq

>>>>

There is a slight complication in the formula for computing $\Delta J_r/J_r$ and $\Delta L_z/L_z$.
In a moment we will consider the effect of an inaccuracy in the distance from
the Sun to the Galactic center on actions. However, this inaccuracy induces an
error in $x$, or $\Delta x$. This is not the same as an inaccuracy in $\Delta
R$, but they are related by the following argument. An error $\Delta x$ will
induce an erroneous radius $R_{\text{err}}$ related by the formula,
\beq
(x+\Delta x)^2 + y^2 = R_{\text{err}}^2\text{.}
\eeq
Keeping only terms to first order in $\Delta x$, we have that,
\beq
\begin{split}
R_{\text{err}}^2 &= R^2 - 2 R \cos{\theta} \Delta x \\
\implies \Delta R &\equiv \abs{R_{\text{err}} - R} = \abs{\cos{\theta}} \Delta x\text{.}
\end{split}
\eeq
Averaging over the circle, we therefore have that
\beq
\avg{\Delta R} = \frac{2}{\pi} \Delta x\text{.}
\eeq
Therefore, the error in $J_r$ and $L_z$ are related to $\Delta x$ by,
\beq\label{eq:Jr_epi_dx}
\begin{split}
\frac{\Delta J_r}{J_r} &= \frac{4 \Delta x}{\pi A_R} \\
\frac{\Delta L_z}{L_z} &= \frac{2 \Delta x}{\pi R}\text{.}
\end{split}
\eeq
